Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-09-03 papers/thesis-kirstie/thesis.tex
switch to standard build for papers
make first four plots build with fac
add weights figure to thesis
added more plots to thesis

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{plot_HardSphere_Potential.png}
    \caption{A Hard Sphere Potential is zero for $r>2R$, and infinity for $r\leq{2R}$ which is approximately 1.225 in this example.}
    \label{fig:HardSphere_potential}
  \end{figure}
\[{}\]
\[{}\]
\[{}\]
\[{}\]

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{LJ_Potential.png}
    \caption{Leonard-Jones Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{LJ_Potential_2part.png}
    \caption{Leanard-Jones Potential broken into two parts for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential_2parts}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{WCA_Potential.png}
    \caption{WCA Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:WCA_potential}
  \end{figure}

@@

Unlike the WCA potential, the erf potential depends on temperature through the parameters $\alpha$ and $\Xi$. Figure \ref{fig:alphaXivsT} shows how $\alpha$ and $\Xi$ vary with temperature when $\sigma=1$ and $\epsilon=1$, and Figure \ref{fig:erf_potential} shows the erf potential at reduced temperatures $\frac{k_BT}{\epsilon}=1$, $\frac{k_BT}{\epsilon}=2$, and $\frac{k_BT}{\epsilon}=3$ alongside the WCA potential. %As seen in Figure \ref{fig:erf_potential}, the erf potentials closely match the WCA potential for reduced temperatures below $\frac{k_BT}{\epsilon}=2$, and for r/$\sigma$ less than ???. % so only values of $V_{erf}$ that are much less than $k_BT$/$\epsilon$ ??? will be considered. 
% In these regions $\alpha$ decreases with increasing temperature, and $\Xi$ increases with increasing temperature.

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=4.5cm]{plot_alpha_vs_KbT.png}
      %\includegraphics[height=5cm]{plot_alpha_vs_KbT.png}
      \caption{$\alpha$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=4.5cm]{plot_xi_vs_KbT.png}
      %\includegraphics[height=5cm]{plot_xi_vs_KbT.png}
      \caption{$\Xi$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \caption{These plots, generated with $\sigma=1$ and $\epsilon=1$, show how the parameters $\alpha$ and $\Xi$ vary with temperature. (a) $\alpha$ decreases with increasing temperature. (b) $\Xi$ rapidly increases for temperatures below $\frac{k_BT}{\epsilon}=52$ and then gradually decreases.}
    \label{fig:alphaXivsT}
    \end{figure}

\begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=7cm]{Verf.png}
    %\includegraphics[height=5cm]{Verf.png}
    \caption{Error Function Potential $V_{erf}(r)$ at several temperatures with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ shown in black.}
    \label{fig:erf_potential}
  \end{figure}

\color{red}\noindent!ADD PLOT of df/dr=w2*w2 !!! BUT not here!\color{black}
\[\]
\[\]

Another way to find values for $\Xi(T)$ is to find computationally the value $\Xi$ for which the second virial coefficient evaluated for the error function potential $V_{erf}(r)$ is equal to the value for the second virial coefficent evalued for the WCA potential $V_{WCA}$, with $\alpha(T)$ plugged into the equation for $B_{2erf}$ at each temperature T. A plot of $\Xi(T)$ obtained through this method is shown in Figure \ref{fig:XifromB2vsT}.
\begin{equation}B_{2erf}(T) =B_{2WCA}(T)\end{equation}
\begin{equation}B_{2erf}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{erf}(r)}-1\right)d\vec{r} \end{equation}
\begin{equation}B_{2erf}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{erf}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]\end{equation}
and 
\begin{equation}B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} \end{equation}

\[\]
\[\]
\[\]

\begin{figure}[h!]
    \centering
    %\includegraphics[height=7cm]{Xi_from_B2.png}
    \caption{Shows the temperature dependence of $\Xi$ generated from matching the second virial coeficients for $V_{erf}(r)$ and $V_{WCA}(r)$ at each temperature.}
    \label{fig:XifromB2vsT}
  \end{figure}
\color{red}
\noindent !ADD PLOT of Verf !!!
\noindent!ADD PLOT of df/dr=w2*w2 !!! BUT not here!
\color{black}
%\[\]
%\[\]

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{Gaussian_Plot.png}
    \caption{A 2D Gaussian Distribution of width 2$\sigma$}
    \label{fig:Gaus_plot}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    % FIXME \includegraphics[height=6cm]{weight_functions.png}
    \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

@@

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{plot_HardSphere_Potential.png}
    \caption{A Hard Sphere Potential is zero for $r>2R$, and infinity for $r\leq{2R}$ which is approximately 1.225 in this example.}
    \label{fig:HardSphere_potential}
  \end{figure}
\[{}\]
\[{}\]
\[{}\]
\[{}\]

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{LJ_Potential.png}
    \caption{Leonard-Jones Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{LJ_Potential_2part.png}
    \caption{Leanard-Jones Potential broken into two parts for $\sigma=1$, $\epsilon=1$}
    \label{fig:LJ_potential_2parts}
  \end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{WCA_Potential.png}
    \caption{WCA Potential for $\sigma=1$, $\epsilon=1$}
    \label{fig:WCA_potential}
  \end{figure}

@@

Unlike the WCA potential, the erf potential depends on temperature through the parameters $\alpha$ and $\Xi$. Figure \ref{fig:alphaXivsT} shows how $\alpha$ and $\Xi$ vary with temperature when $\sigma=1$ and $\epsilon=1$. % and Figure \ref{fig:erf_Potential} shows the erf potential at reduced temperatures $\frac{k_BT}{\epsilon}=1$, $\frac{k_BT}{\epsilon}=2$, and $\frac{k_BT}{\epsilon}=3$ alongside the WCA potential. %As seen in Figure \ref{fig:erf_potential}, the erf potentials closely match the WCA potential for reduced temperatures below $\frac{k_BT}{\epsilon}=2$, and for r/$\sigma$ less than ???. % so only values of $V_{erf}$ that are much less than $k_BT$/$\epsilon$ ??? will be considered. 
% In these regions $\alpha$ decreases with increasing temperature, and $\Xi$ increases with increasing temperature.

 \begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=4.5cm]{plot_alpha.png}
      \includegraphics[height=5cm]{plot_alpha.pdf}
      \caption{$\alpha$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \begin{subfigure}[b]{0.4\linewidth}
      % FIXME \includegraphics[height=4.5cm]{plot_xi.png}
      \includegraphics[height=5cm]{plot_xi.pdf}
      \caption{$\Xi$ versus $k_BT/\epsilon$}
    \end{subfigure} 
    \caption{These plots, generated with $\sigma=1$ and $\epsilon=1$, show how the parameters $\alpha$ and $\Xi$ vary with temperature. (a) $\alpha$ decreases with increasing temperature. (b) $\Xi$ rapidly increases for temperatures below $\frac{k_BT}{\epsilon}=52$ and then gradually decreases.}
    \label{fig:alphaXivsT}
    \end{figure}

%\begin{figure}[h!]
%    \centering
    %\includegraphics[height=7cm]{erf_Potential.pdf}
%    \caption{Error Function Potential $V_{erf}(r)$ at several temperatures with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ shown in black.}
%    \label{fig:erf_Potential}
%  \end{figure}

%\color{red}\noindent!ADD PLOT of df/dr=w2*w2 !!! BUT not here!\color{black}

Another way to find values for $\Xi(T)$ is to find computationally the value $\Xi$ for which the second virial coefficient evaluated for the error function potential $V_{erf}(r)$ is equal to the value for the second virial coefficent evalued for the WCA potential $V_{WCA}$, with $\alpha(T)$ plugged into the equation for $B_{2erf}$ at each temperature T. 
\begin{equation}B_{2erf}(T) =B_{2WCA}(T)\end{equation}
\begin{equation}B_{2erf}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{erf}(r)}-1\right)d\vec{r} \end{equation}
\begin{equation}B_{2erf}(T) = \frac{\pi}{3}\Xi^3\left[\left(\frac{\alpha^3}{\Xi^3}+\frac{3\alpha}{2\Xi}\right)\left(1+\operatorname{erf}\left(\frac{\alpha}{\Xi}\right)\right)+\frac{1}{\sqrt{\pi}}\left(\frac{\alpha^2}{\Xi^2}+1\right)e^{-\left(\frac{\alpha}{\Xi}\right)^2}\right]\end{equation}
and 
\begin{equation}B_{2WCA}=-\frac{1}{2}\int_{Volume}\left(e^{-\beta{V}_{WCA}(r)}-1\right)d\vec{r} \end{equation}
A plot of $\Xi(T)$ obtained through this method is shown in Figure \ref{fig:xi_fromB2vsT}, and Figure \ref{fig:erf_Potential_xifromB2} shows the erf potential at reduced temperatures $\frac{k_BT}{\epsilon}=1$, $\frac{k_BT}{\epsilon}=2$, and $\frac{k_BT}{\epsilon}=3$ alongside the WCA potential.

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{xi_fromB2.pdf}
    \caption{Shows the temperature dependence of $\Xi$ generated from matching the second virial coeficients for $V_{erf}(r)$ and $V_{WCA}(r)$ at each temperature.}
    \label{fig:xi_fromB2vsT}
  \end{figure}
\color{red}

\begin{figure}[h!]
    \centering
    \includegraphics[height=7cm]{erf_Potential_xifromB2.pdf}
    \caption{Error Function Potential $V_{erf}(r)$ at several temperatures with $\sigma=1$, $\epsilon=1$, compared to the WCA potential $V_{WCA}(r)$ shown in black.}
    \label{fig:erf_Potential_xifromB2}
  \end{figure}

\noindent!ADD PLOT of df/dr=w2*w2 !!! BUT not here!
\color{black}
%\[\]
%\[\]

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{Gaussian}
    \caption{A 2D Gaussian Distribution of width 2$\sigma$}
    \label{fig:Gaus_plot}
  \end{figure}

@@

 \begin{figure}[h!]
    \centering
    \includegraphics[height=6cm]{weight_functions.pdf}
    \caption{Shows how the weight functions $w_0$, $w_1$, $w_2$, $w_3$ vary along the z-axis for a reduced temperature of 2}
    \label{fig:weight_functions}
  \end{figure}

@@

\cite{fake}

\bibliography{thesis}
\bibliographystyle{plain}
